### 2014-11-18 docs/ms.Rmd
Slight spelling and grammer changes and slight rewording of various places. Nothing big

## Introduction
Generations of biologists have endeavored to explain the mechanisms and functions of animal and plant colouration [@thayer_concealing_1909; @poulton_colours_1890; @wallace_natural_1891]. For scientists of this discipline, identifying best practice in measuring colour and colour pattern has been a great challenge. For these biologists, identifying best practice in measuring color and color pattern has been a great challenge. Over the past 150 years, biologists have developed and adapted techniques that are now widespread, including spectrometry, photography, and visual modelling.

The application of spectrometry to biological questions revolutionized the field [@dyck_determination_1966]. Before its widespread use, researchers assigned categorical colour descriptions, arbitrary rankings or scores [e.g. @aldrich_ecogeographic_1991; @bailey_latitudinal_1978; @wheelwright_colors_1985] or matched paint swatches or munsell chip ratings based on their own visual assessment [e.g. @burtt_analysis_1986; @key_temperature_1954]. Although no doubt applied carefully, these techniques limited progress. For example, many researchers designed colour assessment methods specifically for their projects [e.g. @aldrich_ecogeographic_1991; @bailey_latitudinal_1978] rendering data by incomparable across studies. This is especially problematic when different measurement techniques are used on the same species [e.g. the house finch _Carpodacus mexicanus_; @aldrich_origin_1978; @hill_female_1990]. Likewise, because human vision is inherently different to most other animals [@bennett_sexual_1994; @douglas_spectral_2014], its use can lead to erroneous conclusions [@bennett_sexual_1994; @endler_measurement_1990].

@@

Although relatively easy to implement and potentially powerful, sensory models are built on multiple assumptions about the way in which stimuli are visually and perceptually processed, and these can dramatically shape the results of a given analysis [@lind_avian_2009; @pike_preserving_2012]. For example, Vorobyev et al.’s [-@vorobyev_receptor_1998; @vorobyev_colour_2001] widely used receptor-noise model requires researchers to specify the form of receptor quantum catches (i.e. raw versus log-transformed), the use of any colour constancy mechanism (e.g. von Kries), as well as the photoreceptor signal-to-noise ratios, their relative densities, and the type of noise predominating (i.e. neural and/or receptor noise). These data are only available for a small number of species, such as humans and honeybees, and so assumptions and extrapolations are necessary when models are applied to other species. Unless the biological rationale underlying every parameter choice is clearly understood, justified, and reported, such analyses may become ineffective, especially when comparing results between studies [@pike_preserving_2012].

@@

Our review of recent colour literature highlights some important reporting gaps that will hinder the reproducibility of studies of biological colouration. While we recognize that journals have space limitations and that work may reference previous methological and analytical details, we strongly believe that researchers can do a better job of reporting details which are essential to the transparency and reproducibility of their work.  While all criteria are important, some deserve special attention. In particular, we found that colour scientists could do a better job reporting light sources, the numbers of pixels or spectra averaged, and the type of standards used. More importantly, the probe distance and angle should be standard reporting for all studies using spectrometry. Visual models were regularly used to analyse spectral data, something we welcome. However, there were many important aspects of the analysis that were seldom reported, including the type of quantum catch used, whether photoreceptor adaptation was modelled and the type of neural noise used in receptor-noise models. Photoreceptor densities should also be reported where possible even if using standard avian photorecptor densities. These all have important consequences on downstream analysis and the reproducibility of colour signal quantification [e.g. @kemp_ornamental_2008; @santos_comparison_2007]. It is said that a picture is worth 1000 words, and we recommend the presentation of spectral reflectance curves where possible; these figures are visually appealing and allow for the rapid assesment of the nature and quality of the data, independent of downstream processing. Surprisingly, we found that only `r round(fig, digits = 2)`% of studies using spectral reflectance data had a figure showing these curves. When possible, we also recommend that authors justify data capture and analytical approaches - something few studies we investigated explicitly outlined.

Our objective in this paper was not to point out single studies, but to highlight an important gap in reporting that can influence the reproducibility of colour research and cross-study comparisons. By no means do we wish to say that studies lacking important details are not of significant value. Indeed, even in our own work [e.g. @umbers_bright_2013] we have failed to report important details, which in retrospect can lead to confusion about how such data were collected and analysed. This review of reporting is aimed at providing constructive criticism; it is only through critical appraisal and collegial discussion that we can identify such gaps as areas for improvement, and constructively contribute to the growth of our field. Such assessments are particularly important in an age where accountability, transparency and reproducibility are of utmost importance.

We believe that part of the issue at hand is simply that many researchers seldom have clear guidelines to follow when undertaking research, and may overlook outlining important aspects of methodology and analysis.We hope our critical evaluation of recent literature has highlighted a need for more careful description of how colour signals have been measured and analyzed. We are optimistic that this may help establish uniform reporting guidelines for publication, and to continue the advance of an exciting era in colour research.

>>>>

## Introduction
Generations of biologists have endeavored to explain the mechanisms and functions of animal and plant colouration [@thayer_concealing_1909; @poulton_colours_1890; @wallace_natural_1891]. For these biologists, identifying best practices in measuring colour and colour pattern has been a great challenge. Over the past 150 years, biologists have developed and adapted techniques that are now widespread, including spectrometry, photography, and visual modelling.

The application of spectrometry to biological questions revolutionized the field [@dyck_determination_1966]. Before its widespread use, researchers assigned categorical colour descriptions, arbitrary rankings or scores [e.g. @aldrich_ecogeographic_1991; @bailey_latitudinal_1978; @wheelwright_colors_1985] or matched paint swatches or munsell chip ratings based on their own visual assessment [e.g. @burtt_analysis_1986; @key_temperature_1954]. Although no doubt applied carefully, these techniques limited progress. For example, many researchers designed colour assessment methods specifically for their projects [e.g. @aldrich_ecogeographic_1991; @bailey_latitudinal_1978] rendering data incomparable across studies. This is especially problematic when different measurement techniques are used on the same species [e.g. the house finch _Carpodacus mexicanus_; @aldrich_origin_1978; @hill_female_1990]. Likewise, because human vision is inherently different to most other animals [@bennett_sexual_1994; @douglas_spectral_2014], its use can lead to erroneous conclusions [@bennett_sexual_1994; @endler_measurement_1990].

@@

Although relatively easy to implement, and potentially powerful, sensory models are built on multiple assumptions about the way in which stimuli are visually and perceptually processed and these can dramatically shape the results of a given analysis [@lind_avian_2009; @pike_preserving_2012]. For example, Vorobyev et al.’s [-@vorobyev_receptor_1998; @vorobyev_colour_2001] widely used receptor-noise model requires researchers to specify the form of receptor quantum catches (i.e. raw versus log-transformed), the use of any colour constancy mechanism (e.g. von Kries), as well as the photoreceptor signal-to-noise ratios, their relative densities, and the type of noise predominating (i.e. neural and/or receptor noise). These data are only available for a small number of species, such as humans and honeybees, and so assumptions and extrapolations are necessary when models are applied to other species. Unless the biological rationale underlying every parameter choice is clearly understood, justified, and reported, such analyses may become ineffective, especially when comparing results between studies [@pike_preserving_2012].

@@

Our review of recent colour literature highlights some important reporting gaps that will hinder the reproducibility of studies of biological colouration. While we recognize that journals have space limitations and that work may reference previous methological and analytical details, we strongly believe that researchers can do a better job of reporting details which are essential to the transparency and reproducibility of their work.  While all criteria are important, some deserve special attention. In particular, we found that colour scientists could do a better job reporting light sources, the numbers of pixels or spectra averaged, and the type of standards used. More importantly, the probe distance and angle should be standard reporting for all studies using spectrophometry. Visual models were regularly used to analyse spectral data, something we welcome. However, there were many important aspects of the analysis that were seldom reported, including the type of quantum catch used, whether photoreceptor adaptation was modelled and the type of neural noise used in receptor-noise models. Photoreceptor densities should also be reported where possible even if using standard avian photorecptor densities. These all have important consequences on downstream analysis and the reproducibility of colour signal quantification [e.g. @kemp_ornamental_2008; @santos_comparison_2007]. It is said that a picture is worth 1000 words, and we recommend the presentation of spectral reflectance curves where possible; these figures are visually appealing and allow for the rapid assesment of the nature and quality of the data, independent of downstream processing. Surprisingly, we found that only `r round(fig, digits = 2)`% of studies using spectral reflectance data had a figure showing these curves. When possible, we also recommend that authors justify data capture and analytical approaches - something few studies we investigated explicitly outlined.

Our objective in this paper was not to point out negative aspects of single studies, but to highlight an important gap in reporting that can influence the reproducibility of colour research and cross-study comparisons. By no means do we wish to say that studies lacking important details are not of significant value. Indeed, even in our own work [e.g. @umbers_bright_2013] we have failed to report important details, which in retrospect can lead to confusion about how such data were collected and analysed. This review of reporting is aimed at providing constructive criticism; it is only through critical appraisal and collegial discussion that we can identify such gaps as areas for improvement, and constructively contribute to the growth of our field. Such assessments are particularly important in an age where accountability, transparency and reproducibility are of utmost importance.

We believe that part of the issue at hand is simply that many researchers seldom have clear guidelines to follow when undertaking research, and may overlook outlining important aspects of methodology and analysis. We hope our critical evaluation of recent literature has highlighted a need for more careful description of how colour signals have been measured and analyzed. We are optimistic that this may help establish uniform reporting guidelines for publication, and to continue the advance of an exciting era in colour research.
